---
title: "Lab 6, Exercise 8: Create a data graphic"
subtitle: "SDS 192"
author: "Katelyn Diaz"
date: "`r format(Sys.Date(), '%B %e, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    fig_width: 7
    fig_height: 6
    fig_caption: true
    theme: lumen
    df_print: paged
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  echo = TRUE
)
library(tidyverse)
library(sds192)
```

### Exercise 8: Use ggplot2 and group_by() to create an interesting and informative data graphic. It need not be about baby names. Post your graphic and a short description of it to Slack.
```{r, fig.cap = "Katelyn Diaz"}
diamonds

diamond_plot <- ggplot(diamonds, aes(x= clarity, y = price, color = clarity))+
  ggtitle("Price of diamonds depending on clarity and color") +
  ylab("Price ($)") +
  xlab("Color of diamond, D=Colorless") +
  # fig.cap = "Katelyn Diaz" +
  geom_violin() +
 # geom_point() +
 # geom_smooth() +
  facet_wrap(~color)+
  theme_economist()+
  scale_fill_distiller(palette = "Blues")
diamond_plot
```






## Word count

```{r word_count, message=FALSE, echo=FALSE}
text_stats()
```

## Standards

In this assignment, we attempted the following [standards](https://beanumber.github.io/sds192/standards.html):

- `r standard_button("markdown")`: We met the Markdown standard because we...
- `r standard_button("aesthetics")`: We met the Aesthetics standard because we...


