---
title: "Lab Name"
author: "Author Name"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
library(babynames)
```

### Exercise 1: In which year was that name given to M and F babies most equally (i.e. closest to a 50/50 split)?

1956 (proportion closest to .5)

```{r}
babynames %>%
  filter(name == "Jackie") %>%
  group_by(year) %>%
  summarize(
    num_sexes = n(), 
    total = sum(n), 
    boys = sum(ifelse(sex == "M", n, 0)),
    girls = total - boys,
    girl_pct = girls / total
  )

```

### Exercise 2: Which year had the greatest number of births?
```{r}
babynames %>%
  group_by(year) %>%
   # group by year just groups everything by year. all the info for that single year. N = number of babies with that certain name (ie elizabeth)
  summarise(
    # compresses your data by what you told it to do
    num_births = sum(n)
    # adding/grouping all of the n's for a specific year, ie all the names from 1880 were added together, to equal the number of kids born that year
  ) %>% 
 
     arrange (desc(num_births))

```

### Exercise 3: In a single pipeline, compute the earliest and latest year that each name appears

```{r}
babynames %>%
  group_by(name) %>%
  summarize(
    min_year = min(year), 
    max_year = max(year)
    # bu calling a variable like this, your variable won't be "global"
  )
```

### Exercise 4: There are 15 names that have been assigned to both sexes in all 138 years. List them.

```{r}
# babynames %>%
#   group_by(name) %>%
#   summarise(
#     total = sum(n), 
#     num_girl = sum(ifelse(sex == "F", n, 0)),
#     num_boys = sum(ifelse(sex == "M", n, 0)),
#    # num_sex = sum(ifelse(num_sexes == 2, n, 0))
#   ) %>%
#   filter (years_used == "138") %>%
#   filter (num_girls > 138)
```

### Exercise 5: Among popular names (let’s say at least 1% of the births in a given year), which name is the youngest—meaning that its first appearance as a popular name is the most recent?
```{r}
popular <- babynames %>%
  mutate (popular = prop >= .01) %>%
  # use one equal sign if you're creating the variable there and its the first time you're using it
  filter(popular == TRUE) %>%
  group_by(name) %>%
  summarize(
    first_time = min(year)
  )

popular %>%
  arrange(desc(first_time))
```

### Exercise 8: Use ggplot2 and group_by() to create an interesting and informative data graphic. It need not be about baby names. Post your graphic and a short description of it to Slack.
```{r}

babynames_plot <- babynames %>%
  
  
  
my_storms <- storms %>%
    filter(year == 1995)
my_storms <- ggplot(data = my_storms, aes(group = name, x=long, y=lat, color = wind)) +
  geom_line()
my_storms +
  facet_wrap(~name) +
  scale_fill_distiller(palette = "Blues")
# glimpse(diamonds)
# 
# diamond_plot <- diamonds %>%
#   mutate(cut =)
# 
#   ggplot(diamonds, aes(y= price, x = carat))+
#   facet_wrap(cut) +
#   geom_boxplot()
# diamond_plot
#                        
#   filter(popular == TRUE) %>%
#   group_by(cut) %>%
#   summarize(
#     first_time = min(year)
#   )
# 
# 
# 
# 
# home_plot <- ggplot(housing, aes(y = State, x = Home.Price.Index)) + 
#   geom_vline(xintercept = 1, linetype = "longdash", color = "black") +
#   geom_point(aes(color = Date),
#              alpha = 0.3,
#              size = 1.5,
#              position = position_jitter(width = 0, height = 0.25))
# home_plot + 
#   scale_color_continuous(breaks = c(1975.25, 1994.25, 2013.25),
#                          labels = c(1971, 1994, 2013))
```



...

