---
title: "Single-Table Analysis with dplyr"
author: "Katelyn Diaz"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
library(babynames)
# head means that it will show you the first few rows of that data set
head(babynames)

```

``` {r}
# Find a subset of the columns using select():
babynames %>%
  select(year, name, n) %>%
  head()

# Find a subset of the rows using filter():
babynames %>%
  filter(name == "Bella") %>%
  head()

# Do both and assign the result to a new object:
bella <- babynames %>%
  filter(name == "Bella") %>%
  select(year, name, sex, n)

# Check the dimensions of that object, view the first few rows, and verify what kind of object it is:
dim(bella)
head(bella)
class(bella)

# Note that bella is a tbl_df, a tbl, and a data.frame. Objects in R can have more than one type!
# Let’s make a quick plot of the popularity of Bella over time.
library(ggplot2)
ggplot(data = bella, aes(x = year, y = n)) + 
  geom_line(aes(color = sex))

# Use mutate() to create new variables. Here, we define a variable called popular that is TRUE if the name was assigned to more than 1% of all babies in that year.
babynames <- babynames %>%
  mutate(popular = prop > 0.01)

# Use rename() to rename a variable:
babynames <- babynames %>%
  rename(is_popular = popular)

# Use the new variable (and filter()) to create a subset of the rows:
popular <- babynames %>%
  filter(is_popular)
nrow(popular)
head(popular)

# What are the single most popular names of all time? To find them we can arrange() the table in descending order of the proportion of babies who got that name.
popular %>%
  arrange(desc(prop))

```

### Exercise 1: What does the value of the prop column in the first line of output above mean? Write one sentence to explain what it means to someone who has never taken a statistics course.

Proportion of how often the name is used. i.e. in 1880, 0.0815 of the boys were named John

### Exercise 2: Choose a name, and find the year in which that name was used most frequently.

```{r exercise 2}
babynames %>%
  filter (name == "Elizabeth") %>%
  arrange(desc(prop))
  

```

### What was the most popular name that year? (year 1880)
```{r}
babynames %>%
filter(year == 1880) %>%
  arrange(desc(prop))
```

### Exercise 4: In which year was that name given to M and F babies most equally (i.e. closest to a 50/50 split)?
```{r}
bella %>%
  summarize(num_rows = n(), most_bellas = max(n))
```

### Exercise 5: What does the value of num_rows represent (in real-world terms) in the previous result? Explain what it means to your neighbor and argue about it until you agree.
It shows the number of years that there has been 5121 Bellas.

### Exercise 6: Re-write the following expression using the pipe operator:
arrange(select(filter(babynames, name == "Jordan"), -name), desc(prop))


```{r}
babynames %>%
  filter (name == "Jordan") %>%
  select (-name) %>%
  arrange (desc(prop))

```


...
